Fermi and eROSITA bubbles

### 2021-10-23 paper.tex
update

\item Isothermal atmosphere:
  \begin{enumerate}
     \item $T_{\text{atmp}}=10^{6}$ K. \citep{temperature-MW}
     \item Density:
          \begin{equation}
             \rho_{\text{atmp}}=\rho_{\text{atmp}}^{\text{peak}}
             \exp\left[-\frac{\Phi_{\text{bulge}}}{k_{B}T_{\text{atmp}}/m}\right],
             \label{atmosphere-density}
          \end{equation}
          where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
          and gravitational potential are continuous at the interface between disk and atmosphere (i.e. $z=\pm z_{0}$).
  \end{enumerate}

>>>>

\item Isothermal atmosphere:
  \begin{enumerate}
     \item $T_{\text{atmp}}=10^{6}$ K. \citep{temperature-MW}
     \item Density:
          \begin{equation}
             \rho_{\text{atmp}}=\rho_{\text{atmp}}^{\text{peak}}
             \exp\left[-\frac{\Phi_{\text{bulge}}}{k_{B}T_{\text{atmp}}/m}\right],
             \label{atmosphere-density}
          \end{equation}
          where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
          and gravitational potential are continuous at the interface ($z=\pm z_{0}$) between disk and atmosphere.
  \end{enumerate}
